\documentclass[12pt]{article}

\title{Phase 10}
\author{Joharah Seguerra \\ Michael Tran}
\date{\today}

\begin{document}
\maketitle

\section{Introduction}

This is a Java implementation of the card game Phase 10. This program is meant for four
players; the main player, and three CPUs.

\subsection{Cards}
\begin{itemize}
	\item There are four colors for the numbered cards: red, blue, yellow, and green.
	\item Cards are numbered one through twelve, and there are two of each per color.
	\item Four skip cards
	\item Eight wild cards
\end{itemize}

\subsubsection{Card functionality}

\begin{itemize}
	\item Wild cards are substitutes for a card in a phase.
	\item Skip cards are used to skip the next player's turn. The CPU automatically chooses the
player with the smallest amount of cards to skip, excluding itself. Skip cards cannot be
picked up from the discard pile. If the first card in the discard pile at the start of a
game is a skip card, the first player loses his turn.
Skip cards cannot be hit into the middle pile and they cannot be used like wild cards to
complete a phase.
	\item Cards in played phases cannot be picked up.
\end{itemize}

\subsection{Phases}
The default phases are the following:
\begin{itemize}
	\item 1. 2 sets of 3
	\item 2. 1 set of 3 + 1 run of 4
	\item 3. 1 set of 4 + 1 run of 4
	\item 4. 1 run of 7
	\item 5. 1 run of 8
	\item 6. 1 run of 9
	\item 7. 2 sets of 4
	\item 8. 7 cards of one color
	\item 9. 1 set of 5 + 1 set of 2
\end{itemize}

A set is cards of the same number. A run is a sequential set of numbers.
One must complete a phase to advance. If a phase has multiple combinations of cards, they
must all be played.

\section{Gameplay}
This program allows for one human player and three CPU players.
The player to the dealer's left starts. Turns are in a clockwise direction.

Players start off their turn with choosing a card either from the discard or draw pile.
If the player is able to make a phase, he can play the cards and hit during the same
turn. Players end their turn by discarding a card into the discard pile.

Rounds are played until someone completes their phase and empties their entire deck.
Scores are computed according to the following:

\begin{itemize}
	\item Cards numbered 1-9 are worth 5 points each.
	\item Cards numbered 10-12 are worth 10 points each.
	\item Skips and wilds are worth 25 points each.
\end{itemize}

A new hand is dealt out after a round is ended. All cards are gathered in the draw pile,
shuffled, and each person is dealt 10 cards.

If one has not advanced to their next phase, they must resume working on their current
phase.

\subsection{Hitting}
One can hit cards from their deck onto the middle piles from finished phases. These cards
must match the piles. Cards must fit in a number run properly for it to be a valid hit.

\subsection{Winning}
The winner is the person with the lowest score and has completed ten phases.

\end{document}
